### 2010-03-17 papers/icfp-2010-desc/paper_desc_levitation.tex
IDesc@ICFP: clarify switchD elaboration.

The entire work of the magician stands here, in this extension. One
could be worried by the availability of such operations in our type
theory. Indeed, it would be inconvenient for the user to have to
decide between two variants. In fact, we give no choice to the user,
hence no inconvenience. Just as the $\F{switch}$ operator was sealed
off by the type propagation machinery, $\F{switchD}$ is not provided
to the user. We simply extend the type-checking rules
(Fig.~\ref{fig:type-checking}) with the following inference rule:

>>>>

The entire work of the magician stands here, in this extension. One
could be worried by the availability of such operations in our type
theory. Indeed, it would be inconvenient for the user to have to
decide between two variants. The solution to this problem stands, once
again, in the type propagation system. Just as the $\F{switch}$
operator, $\F{switchD}$ can be automatically elaborated. To this end,
we simply extend the type-checking rules
(Fig.~\ref{fig:type-checking}) with the following inference rule:
